Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-01-12 manuscript/manuscript.Rmd
updated figs

```{r figure_2, dependson="plot-options", fig.cap="Simulated changes species' median cover caused by a 1% increase in observed precipitation or temperature. We used the median of simulated results because the average was highly influence by some extreme outliers.", fig.width=4.5, fig.height=4, cache=FALSE, results='hide'}
climBase <- readRDS("../montana/quadBM/simulations/climateChangeBase.rds")
climPpt <- readRDS("../montana/quadBM/simulations/climateChangePrecip.rds")
climTemp <- readRDS("../montana/quadBM/simulations/climateChangeTemperature.rds")
climBoth <- readRDS("../montana/quadBM/simulations/climateChangePptTmp.rds")
climBase$sim <- rep("Observed", nrow(climBase)) 
climPpt$sim <- rep("Precipitation", nrow(climBase)) 
climTemp$sim <- rep("Temperature", nrow(climBase)) 
climBoth$sim <- rep("Both", nrow(climBase)) 
climSimsQBM <- rbind(climBase, climPpt, climTemp, climBoth)
# ggplot(climSimsQBM)+
#   geom_boxplot(aes(x=species, y=cover*100, fill=sim))+
#   scale_y_continuous(limits=c(0,10))
climSimsQBMavg <- ddply(climSimsQBM, .(sim, species), summarise,
                        avgCover = median(cover))
climSimQBMcast <- dcast(climSimsQBMavg, formula = species~sim)
climSimQBMcast$diffP <- with(climSimQBMcast, (Precipitation*100)-(Observed*100)) 
climSimQBMcast$diffT <- with(climSimQBMcast, (Temperature*100)-(Observed*100))
climSimQBMcast$diffB <- with(climSimQBMcast, (Both*100)-(Observed*100))
climSimQBMplot <- melt(climSimQBMcast)
ggplot(data=subset(climSimQBMplot, variable=="diffP"|variable=="diffT"|variable=="diffB"))+
  geom_bar(aes(x=species, y=value, fill=variable), stat="identity", position="dodge", color="white")+
  scale_fill_manual(name="", labels=c("1% Precipitation Increase", "1% Temperature Increase", "1% Temp. & Ppt. Increase"), values=c("grey25", "grey50", "grey75"))+
  theme_bw()+
  theme(legend.position=c(0.6, 0.8))+
  ylab("Cover Change (%)")+
  xlab("Species")
```

>>>>

```{r figure_2, dependson="plot-options", fig.cap="Simulated changes species' median cover caused by a 1% increase in observed precipitation or temperature. We used the median of simulated results because the average was highly influence by some extreme outliers.", fig.width=4.5, fig.height=4, cache=FALSE, results='hide'}
climBase <- readRDS("../montana/quadBM/simulations/climateChangeBase.rds")
climPpt <- readRDS("../montana/quadBM/simulations/climateChangePrecip.rds")
climTemp <- readRDS("../montana/quadBM/simulations/climateChangeTemperature.rds")
climBoth <- readRDS("../montana/quadBM/simulations/climateChangePptTmp.rds")
climBase$sim <- rep("Observed", nrow(climBase)) 
climPpt$sim <- rep("Precipitation", nrow(climBase)) 
climTemp$sim <- rep("Temperature", nrow(climBase)) 
climBoth$sim <- rep("Both", nrow(climBase)) 
climSimsQBM <- rbind(climBase, climPpt, climTemp, climBoth)
# ggplot(climSimsQBM)+
#   geom_boxplot(aes(x=species, y=cover*100, fill=sim))+
#   scale_y_continuous(limits=c(0,10))
climSimsQBMavg <- ddply(climSimsQBM, .(sim, species), summarise,
                        avgCover = median(cover))
climSimQBMcast <- dcast(climSimsQBMavg, formula = species~sim)
climSimQBMcast$diffP <- with(climSimQBMcast, (Precipitation*100)-(Observed*100)) 
climSimQBMcast$diffT <- with(climSimQBMcast, (Temperature*100)-(Observed*100))
climSimQBMcast$diffB <- with(climSimQBMcast, (Both*100)-(Observed*100))
climSimQBMplot <- melt(climSimQBMcast)
myCols2 <- c("#277BA8", "#7ABBBD", "#AED77A")
ggplot(data=subset(climSimQBMplot, variable=="diffP"|variable=="diffT"|variable=="diffB"))+
  geom_bar(aes(x=species, y=value, fill=variable), stat="identity", position="dodge", color="white")+
  scale_fill_manual(name="", labels=c("1% Precipitation Increase", "1% Temperature Increase", "1% Temp. & Ppt. Increase"), values=myCols2)+
  theme_bw()+
  theme(legend.position=c(0.6, 0.8))+
  ylab("Cover Change (%)")+
  xlab("Species")
```
